### 2019-09-11 scache/tii/tex/intro.tex
Revision for re-submit.

The rest of the paper is organized as follows:
% We discuss the opportunities to optimize shuffle in Section \ref{motivation}.
Section \ref{opt} presents the detail of methodologies which using by SCache to gain shuffle optimization, including two heuristic algorithms and a co-scheduler.
We present the implementation of SCache in Section \ref{impl} and do comprehensive evaluations in Section \ref{evaluation}.
We discuss some related work in Section \ref{related} and conclude in Section \ref{conclusion}.
}

>>>>

The rest of the paper is organized as follows:
{\color{blue}
% We discuss the opportunities to optimize shuffle in Section \ref{motivation}.
We present the methodologies of optimization which using by SCache in Section \ref{opt} and detail the implementation of SCache in Section \ref{impl}.
We introduce the FRQ performance model in Section \ref{model}.
In Section \ref{evaluation}, we present comprehensive evaluations about SCache and the FRQ model.
% We present the implementation of SCache in Section \ref{impl} and do comprehensive evaluations in Section \ref{evaluation}.
We also discuss the related work in Section \ref{related} and conclude in Section \ref{conclusion}.
}
}

### 2019-09-11 scache/tii/tex/model.tex
Revision for re-submit.

In this section, we introduce \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
% The FRQ model quantifies computing and I/O resources and visualizes them in the time dimension.
In the industrial production, the FRQ model is able to predict the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, etc.
% The FRQ model assist us in analyzing the resource scheduling of DAG framework and evaluate their performance.
We first introduce the FRQ model in Subsection \ref{model_overview}. In the following Subsection \ref{model_analysis}, we use the FRQ model to describe three different computation jobs and analyze their performance. In the last Subsection \ref{model_evaluation}, we use the actual experimental results to evaluate the FRQ model.

\subsection{The FRQ Model}\label{model_overview}
% The current distributed computing frameworks mostly use DAGs to describe the computation logic. 
% A shuffle phase is required between each adjacent DAG computation phases.
To better analyze the relationship between the computation phase and the shuffle phase, we propose the FRQ model. After quantifying computing and I/O resources, the FRQ model can describe different resource scheduling strategies. For convenience, we introduce the FRQ model by taking a simple MapReduce job as an example in this section.

Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce task. The FRQ model has five input parameters:
\begin{itemize}
	\item Input Data Size \((D)\): The  Input data size of the job.
	\item Data Conversion Rate \((R)\): The conversion rate of the input data to the shuffle data during a computation phase.
	% This rate depends on the algorithm used in the computation phase.
    \item Computation Round Number \((N)\): The number of rounds needed to complete the computation phase. These rounds depend on the current computation resources and the configuration of the framework. Take Hadoop MapReduce as an example. Suppose we have a cluster with 50 CPUs and enough memory, the map phase consists of 200 map tasks, and each map requires 1 CPU. Then we need 4 rounds of computation to complete the map phase.
    \item Computation Speed \((V_{i})\): 
	The computation speed for each computation phase.
	% This speed depends on the algorithm used in the computation phase.
    \item Shuffle Speed \((V_{Shuffle})\): 
	Transmission speed in the shuffle phase.
	% This speed depends on network and storage device bandwidth.
\end{itemize}

@@

The FRQ model calculates the execution time of each phase of the job with these five parameters. As shown in Figure \ref{fig:model_basic}, the total execution time of a job is the sum of the map phase time and reduce phase time:
% \(T_{Job}=T_{Map}+T_{Reduce}\).
\begin{equation}
\label{equation_Tjob}
\begin{aligned}
    T_{Job} &= T_{Map} + T_{Reduce}
\end{aligned}
\end{equation}

@@

\(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time of a reduce phase, and (\(K \times T_{P\_Shuffle}\)) represents the computing overhead.
We use \(T_{P\_Shuffle}\) to represent the overlap time between the shuffle phase and the reduce phase. \(T_{Shuffle}\) represents the total time of the shuffle phase. 
% The relationship between \(T_{P\_Shuffle}\) and \(T_{Shuffle}\) is determined by the resources scheduling strategy of DAG frameworks. This relationship will be shown in the following Subsection \ref{model_analysis}.  
\(K\) is an empirical value. 
Because the computation of the reduce phase relies on the data transfer results of the shuffle phase, a portion of the computation in the reduce phase needs to wait for the transfer results. This waiting causes the overhead. The FRQ model uses K to indicate the extent of the waiting.

@@

According to Equation \ref{equation_Tjob}\&\ref{equation_Treduce}, we can optimize the job completion time by reducing \(T_{P\_Shuffle}\). Improving I/O speed is an effective way to reduce shuffle time. Another optimization method is to use the idle I/O resources in the map phase for pre-fetching (see Figure \ref{fig:model_basic}). Both of the above methods can effectively reduce \(T_{P\_Shuffle}\). 
% By using the FRQ model to describe a MapReduce job, the users can analyze the resource scheduling strategy of the computation framework.

@@

Figure \ref{fig:model_hadoop} shows a scheduling strategy which is used by Hadoop MapReduce. In this scheduling strategy, shuffle phase and reduce phase start at the same time. In this case, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\). Due to the increase in \(T_{P\_Shuffle}\), the time of reduce phase increases (according to Equation \ref{equation_Treduce}). Because the shuffle phase and the computation phase are executed in parallel, the total execution time of a job is the sum of \(T_{Map}\) and \(T_{Reduce}\) (see Equation \ref{equation_Tjob}). The execution time of the shuffle phase is hidden in the reduce phase. 
However, we also found that the I/O resource in the map phase is still idle. This scheduling strategy can still be optimized.

@@

% \begin{table}[!t]
\begin{table*}
\centering
\scalebox{0.95}{
	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
	\hline
	&
	\(D\) &	
	\(R\) &	
	\(N\) &	
	\(V_{Map}\) &	
	\(V_{Reduce}\) &	
	\(V_{Shuffle}\) &	
	\(K\) &	
	\(T_{Map}\) &	
	\(T_{Shuffle}\) &	
	\(T_{P\_Shuffle}\) &
	\(T_{Reduce}\) & 
	\(T_{Job}\) & 
	\(Exp T_{Job}\) &
	\(Error\)\\

	\hline
	& 16	& 1	& 2 &	0.65 &	1 &	0.47 &	0.5 &	24.62 &		34.04	 &	21.73 &	26.87 &	51.48	& 55  &		6.39\% \\
	SCache
	& 32	& 1	& 4 &	0.65 &	1 &	0.47 &	0.5 &	49.23 &		68.09	 &	31.16 &	47.58 &	96.81	& 104 & 	6.91\% \\
	& 48	& 1	& 6 &	0.65 &	1 &	0.47 &	0.5 &	73.85 &		102.13 &	40.59 &	68.29 &	142.14	& 151 & 	5.87\% \\
	& 64	& 1	& 8 &	0.65 &	1 &	0.47 &	0.5 &	98.46 &		136.17 &	50.02 &	89.01 &	187.47	& 193 & 	2.87\% \\
	\hline
	& 16	& 1 & 2 &	0.65 &	1 &	0.47 &	0.6 &	24.62 &		34.04	&	34.04	&	36.43	&	61.04	&	73	&	16.38\%	\\
	Legacy
	& 32	& 1 & 4 &	0.65 &	1 &	0.47 &	0.6 &	49.23 &		68.09	&	68.09	&	72.85	&	122.08	&	135	&	9.57\%	\\
	& 48	& 1 & 6 &	0.65 &	1 &	0.47 &	0.6 &	73.85 &		102.13	&	102.13	&	109.28	&	183.12	&	188	&	2.59\%	\\
	& 64	& 1 & 8 &	0.65 &	1 &	0.47 &	0.6 &	98.46 &		136.17	&	136.17	&	145.70	&	244.16	&	249	&	1.94\%	\\
	\hline
	\end{tabular}
}
\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
\caption{\color{black}Hadoop MapReduce on 4 nodes cluster in the FRQ model}
\label{table1}
\end{table*}
% \subsection{Performance Analysis}\label{model_performance_analysis}

% \begin{table*}[!t]
\begin{table*}
\centering
\scalebox{0.95}{
	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
	\hline
	&
	\(D\) &	
	\(R\) &	
	\(N\) &	
	\(V_{Map}\) &	
	\(V_{Reduce}\) &	
	\(V_{Shuffle}\) &	
	\(K\) &	
	\(T_{Map}\) &	
	\(T_{Shuffle}\) &	
	\(T_{P\_Shuffle}\) &
	\(T_{Reduce}\) & 
	\(T_{Job}\) & 
	\(Exp T_{Job}\) &
	\(Error\)\\

	\hline
	& 128	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	111.30 &	91.43	&	18.29	&	96.81	&	208.12	&	232	&	10.29\%	\\
	SCache
	& 256	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	222.61 &	182.86	&	36.57	&	193.63	&	416.24	&	432	&	3.65\%	\\
	& 384	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	333.91 &	274.29	&	54.86	&	290.44	&	624.36	&	685 &	8.85\%	\\
	% & 512	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	445.22 &	365.71	&	91.43	&			&	841.62	&	1135 &	25.85\%	\\
	\hline
	& 128	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	111.30 &	91.43	&	91.43	&	142.53	&	253.83	&	266 &	4.57\%	\\
	Legacy
	& 256	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	222.61 &	182.86	&	182.86	&	285.06	&	507.67	&	524 &	3.12\%	\\
	& 384	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	333.91 &	274.29	&	274.29	&	427.59	&	761.50	&	776 &	1.87\%	\\
	% & 512	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	445.22 &	365.71	&	365.71	&	588.40	&	1033.62	&	1312 &	21.22\%	\\

	\hline
	\end{tabular}
}
\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
\caption{\color{black}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in the FRQ model}
\label{table2}
\end{table*}

\subsection{Model evaluation}\label{model_evaluation}
To evaluate the FRQ model, we run experiments on two environments: (a) 50 Amazon EC2 m4.xlarge nodes cluster; (b) 4 in-house nodes cluster with 128GB memory and 32 cores per node.
We run the Terasort as an experimental application on a Hadoop MapReduce framework.
% We deployed Hadoop with SCache and without SCache in both environments.

Table \ref{table1} shows the results of the FRQ model in the in-house environment.
% The workload is from 16 GB to 64 GB. 
\(D\) and \(N\) are set according to the application parameters. We calculate \(R, V_{Map}, V_{Shuffle},\)and \(V_{Reduce}\) according to the environment. We set \(K\) to 0.5 and 0.6, which reflects that \(T_{P\_Shuffle}\) has less impact on the reduce phase when enabling SCache. 
% The formulas of \(T_{Job}, T_{Map}, T_{Reduce}\) and \(T_{Shuffle}\) are according to Equation \ref{equation_Tjob}, Equation \ref{equation_Tmap}, Equation \ref{equation_Treduce} and Equation \ref{equation_Tshuffle}, respectively. 
In the Hadoop with SCache, Terasort satisfies the situation in Figure \ref{fig:model_basic} (\(V_{Map} \times R \ge V_{Shuffle}\)). 
% thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle1}.
In the original Hadoop, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\)(see Equation \ref{equation_Tmap}). \(ExpT_{Job}\) represents the actual experiment data, we calculate \(Error\) according to \(T_{Job}\) and \(ExpT_{Job}\). 
% The formula of \(Error\) is:
% \begin{equation}
% 	\label{equation_error}
% 	\begin{aligned}
% 		Error &= \frac{ExpT_{Job} - T_{Job}}{T_{Job}}
% 	\end{aligned}
% \end{equation}

Table \ref{table2} shows the results in Amazon EC2 environment.
% \;\(V_{Map}, V_{Shuffle},\) and \(V_{Reduce}\) are modified because of the different hardware devices.
We set K to the same empirical value.
% The formulas in the table are all the same except \(T_{P\_Shuffle}\).
In this environment, Terasort on Hadoop MapReduce satisfies the situation in Figure \ref{fig:model_scache2} (\(V_{Map} \times R < V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle2}. 
% In the previous case, \(T_{P\_Shuffle}\) is still equal to \(T_{Shuffle}\).

% \begin{figure}
% 	\centering
% 	\begin{subfigure}{0.49\linewidth}
% 		\includegraphics[width=\linewidth]{fig/hadoop_net1}
% 		\caption{\color{black}If \(V_{Map} \times R \ge V_{Shuffle}\)}
% 		\label{fig:hadoop_net1}
% 	\end{subfigure}
% 	\begin{subfigure}{0.49\linewidth}
% 		\includegraphics[width=\linewidth]{fig/hadoop_net2}
% 		\caption{\color{black}If \(V_{Map} \times R < V_{Shuffle}\)}
% 		\label{fig:hadoop_net2}
% 	\end{subfigure}
% 	\caption{\color{black}Network utilization on Hadoop MapReduce with SCache}
% 	\label{fig:hadoop_net}
% \end{figure}

% In order to evaluate the two cases as mentioned above when using SCache, we monitor the network utilization as Figure \ref{fig:hadoop_net}. Figure \ref{fig:hadoop_net1} shows that, in the in-house environment, the network utilization remains high until the shuffle phase is completed. On the other hand, Figure \ref{fig:hadoop_net2} shows that the network utilization has 5 regular peaks in Amazon EC2 environment. 
% Both these two situations are consistent with the FRQ model in Figure \ref{fig:model_scache}. 
% Therefore, we believe that the FRQ model is able to accurately describe the performance of a framework with SCache.

Regarding accuracy, the experimental values are all larger than the calculated values. This is because the application has some extra overhead at runtime, such as network warm-up, the overhead of allocating slots, etc. 
% In the case where the input data is small and the total time is short, the error caused by the overhead is amplified. 
This overhead will be amplified when the input data is small or the total execution time is short. 
Overall, the error between \(T_{Job}\) and \(ExpT_{Job}\) is mainly below 10\%, such errors are acceptable. Therefore, we believe that the FRQ model can accurately describe DAG frameworks.
}

>>>>

In this section, we introduce \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
% The FRQ model quantifies computing and I/O resources and visualizes them in the time dimension.
In the industrial production, the FRQ model is able to predict the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, etc.
% The FRQ model assist us in analyzing the resource scheduling of DAG framework and evaluate their performance.
We first introduce the FRQ model in Subsection \ref{model_overview}. In the following Subsection \ref{model_analysis}, we use the FRQ model to describe different computation jobs and discuss their performance.
% In the last Subsection \ref{model_evaluation}, we use the actual experimental results to evaluate the FRQ model.

\subsection{The FRQ Model}\label{model_overview}
% The current distributed computing frameworks mostly use DAGs to describe the computation logic. 
% A shuffle phase is required between each adjacent DAG computation phases.
{\color{blue}
We propose the FRQ model to better analyze the relationship between the computation phase and the shuffle phase in the DAG computing.
The FRQ model focuses on describing the overhead caused by the shuffle process.
This overhead does not only depends on the input data size, computation speed, complexity of algorithms, and other parameters but also on which scheduling strategy the job takes.
% By using the FRQ model, we can analyze the advantages of each strategy in various situations.
After quantifying computing and I/O resources, the FRQ model can evaluate different resource scheduling strategies by using different formulas.
% For convenience, we introduce the FRQ model by taking a simple MapReduce job as an example in this section.

Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce job. 
As Figure \ref{fig:model_basic} shows, the FRQ model divides the job into three phases: map, shuffle, and reduce.
The horizontal axis represents time and the overlaps between phases represent they execute in parallel.
The FRQ model use these overlaps to describe different scheduling strategies.
For example, as shown in Figure \ref{fig:model_hadoop}, this strategy starts the shuffle phase and the reduce phase at the same time.
And Figure \ref{fig:model_basic} shows the pre-fetching strategy used by SCache. In the pre-fetching strategy, the shuffle phase starts as soon as it can in the map phase.

% As shown in Figure \ref{fig:model_basic}, the FRQ model introduce five parameters:
Firstly, we introduces five input parameters of the FRQ model:
}
\begin{itemize}
	\item Input Data Size \((D)\): The  Input data size of the job.
	\item Data Conversion Rate \((R)\): The conversion rate of the input data to the shuffle data during a computation phase.
	% This rate depends on the algorithm used in the computation phase.
    \item Computation Round Number \((N)\): The number of rounds needed to complete the computation phase. These rounds depend on the current computation resources and the configuration of the framework. Take Hadoop MapReduce as an example. Suppose we have a cluster with 50 CPUs and enough memory, the map phase consists of 200 map tasks, and each map requires 1 CPU. Then we need 4 rounds of computation to complete the map phase.
    \item Computation Speed \((V_{i})\): 
	The computation speed for each computation phase.
	% This speed depends on the algorithm used in the computation phase.
    \item Shuffle Speed \((V_{Shuffle})\): 
	Transmission speed in the shuffle phase.
	% This speed depends on network and storage device bandwidth.
\end{itemize}

@@

The FRQ model calculates the execution time of each phase of the job with these five parameters.
% As shown in Figure \ref{fig:model_basic}
The total execution time of a job is the sum of the map phase time and reduce phase time:
% \(T_{Job}=T_{Map}+T_{Reduce}\).
\begin{equation}
\label{equation_Tjob}
\begin{aligned}
    T_{Job} &= T_{Map} + T_{Reduce}
\end{aligned}
\end{equation}

@@

@@

{\color{blue}
\(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time of a reduce phase, and (\(K \times T_{P\_Shuffle}\)) represents the computing overhead.
\(T_{P\_Shuffle}\) represents the overlap time between the shuffle phase and the reduce phase as shown in Figure \ref{fig:model_basic}. \(T_{Shuffle}\) represents the total time of the shuffle phase. 
% The relationship between \(T_{P\_Shuffle}\) and \(T_{Shuffle}\) is determined by the resources scheduling strategy of DAG frameworks. This relationship will be shown in the following Subsection \ref{model_analysis}.  
\(K\) is an empirical value which represents the overhead caused by shuffle waiting. 
Because the computation of the reduce phase relies on the data transfer results of the shuffle phase, a portion of the computation needs to wait for the transfer results. This waiting causes the overhead.

According to Equation \ref{equation_Tjob}\&\ref{equation_Treduce}, we can optimize the job completion time by reducing \(T_{P\_Shuffle}\).
By using different resource scheduling strategies, the formulas of \(T_{P\_Shuffle}\) are different.
In the next subsection, we show the formulas and discuss the performance of different strategies.
% Improving I/O speed is an effective way to reduce shuffle time. Another optimization method is to use the idle I/O resources in the map phase for pre-fetching (see Figure \ref{fig:model_basic}). Both of the above methods can effectively reduce \(T_{P\_Shuffle}\). 
% By using the FRQ model to describe a MapReduce job, the users can analyze the resource scheduling strategy of the computation framework.
}

@@

Figure \ref{fig:model_hadoop} shows a scheduling strategy which is used by Hadoop MapReduce. In this scheduling strategy, shuffle phase and reduce phase start at the same time. In this case, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\). Due to the increase in \(T_{P\_Shuffle}\), the time of reduce phase increases (according to Equation \ref{equation_Treduce}). Because the shuffle phase and the computation phase are executed in parallel, the total execution time of a job is the sum of \(T_{Map}\) and \(T_{Reduce}\) (see Equation \ref{equation_Tjob}). The execution time of the shuffle phase is hidden in the reduce phase. 
% However, we also found that the I/O resource in the map phase is still idle. This scheduling strategy can still be optimized.

@@
